Hello Window!\\\medskip \large{Felhasználói felület fejlesztés és tesztelés \textit{GTK} környezetben}

### 2011-06-21 book.tex
Fixed table of contents entries of the book.
Fixed index generation of the book.
Reorganized the structure the articles.
Made possible to merge the articles into a book.
Added new title to the book.

\usepackage[a4paper]{geometry}
\geometry{verbose, tmargin=2.0cm, bmargin=2.0cm, lmargin=2.0cm, rmargin=2.0cm}

%hyper references pdf attributes
\usepackage{hyperref}
\hypersetup{
pdftitle={Hello Window!},
pdfauthor={Szilárd Pfeiffer},
pdfsubject={GTK+ and gtkmm programming},
pdfkeywords={szilárd pfeiffer, gtk, gtk+, gtkmm, gnome, hig, linux},
bookmarks={true},
unicode={true},
colorlinks={false},
hyperfigures={true},
a4paper={true}
}

@@

\author{
\href{http://pfeifferszilard.hu}{Pfeiffer Szilárd}
}
\title{Hello Window!}

@@

\chapter{Bevezetés}

\input{article_intro_content}
\input{article_concept_content}
\input{article_basics_content}
\input{article_container_content}
\input{article_window_content}

@@

\addcontentsline{toc}{chapter}{Tartalomjegyzék}
\printindex

\addcontentsline{toc}{chapter}{Táblázatok jegyzéke}
\listoftables

\addcontentsline{toc}{chapter}{Ábrák jegyzéke}
\listoffigures

\addcontentsline{toc}{section}{\lstlistlistingname}
\lstlistoflistings

\addcontentsline{toc}{chapter}{Bibliográfia}
\bibliography{book}
\bibliographystyle{plain}

>>>>

\usepackage[a4paper]{geometry}
\usepackage{makeidx}
\geometry{verbose, tmargin=2.0cm, bmargin=2.0cm, lmargin=2.0cm, rmargin=2.0cm}

%hyper references pdf attributes
\usepackage{hyperref}
\hypersetup{
pdftitle={Hello Window!},
pdfauthor={Pfeiffer Szilárd},
pdfsubject={Felhasználói felület fejlesztés és tesztelés GTK környezetben},
pdfkeywords={szilárd pfeiffer, gtk, gtk+, gtkmm, gnome, hig, linux},
bookmarks={true},
unicode={true},
colorlinks={false},
hyperfigures={true},
a4paper={true}
}

@@

\author{
\href{http://pfeifferszilard.hu}{Pfeiffer Szilárd}
}
\title{
Hello Window!\\\medskip
\large{Felhasználói felület fejlesztés és tesztelés \textit{GTK} környezetben}
}

\makeindex

@@

\part{Bevezetés}

\chapter{Felhasználói felületek létrehozása}
\input{article_intro_gui_content}

\chapter{\textit{Gimp Tool Kit}}
\input{article_intro_gtk_content}

\chapter{A fejlesztés menete}
\input{article_intro_devel_content}

\part{Koncepció}

\chapter{Szignálkezelés dióhéjban}
\input{article_basics_content}

\chapter{Első ablakunk}
\input{article_concept_content}

\part{Alapvető \textit{widget}ek}

\chapter{Konténerek}
\input{article_container_content}

\chapter{Ablakok}
\input{article_window_content}

@@

\newpage
\addcontentsline{toc}{chapter}{Tárgymutató}
\printindex

\newpage
\addcontentsline{toc}{chapter}{Táblázatok jegyzéke}
\listoftables

\newpage
\addcontentsline{toc}{chapter}{Ábrák jegyzéke}
\listoffigures

\newpage
\addcontentsline{toc}{chapter}{\lstlistlistingname}
\lstlistoflistings

\newpage
\addcontentsline{toc}{chapter}{Irodalomjegyzék}
\bibliography{book}
\bibliographystyle{plain}
